\section{Skills learned}
\label{sec:skills}

Throughout the course of this project, several key skills were developed and honed. These skills not only contributed to the successful completion of the project but also provided valuable experience for future endeavors. The following sections outline the primary skills learned:

\subsection{Profiling and performance optimisation}
One of the critical skills acquired was the ability to profile and optimise code. By developing and utilizing a profiler, I was able to identify bottlenecks in the LUA system. This process involved:
\begin{itemize}
    \item Understanding how to use profiling tools to gather performance data.
    \item Analyzing the collected data to pinpoint slow operations.
    \item Implementing optimizations such as prefetching data and precalculating values to enhance performance.
\end{itemize}
These skills are essential for improving the efficiency of any software system.

\subsection{Mathematical modeling and accuracy testing}
Another significant skill developed was the ability to create and test mathematical models. This included:
\begin{itemize}
    \item Isolating parts of the mathematical model to test their accuracy.
    \item Conducting both mathematical and experimental tests to ensure the model met the required accuracy standards.
    \item Implementing algorithms with no bias in estimates, such as the new circle fit algorithm.
\end{itemize}
These skills are crucial for ensuring the reliability and precision of computational models.

\subsection{Advanced algorithm development}
The project also provided experience in developing advanced algorithms. Key aspects included:
\begin{itemize}
    \item Expanding the fitting model to recognize complex shapes, such as the ribbed cylinder of the ILUC.
    \item Ensuring the algorithms were efficient and could be integrated seamlessly into the existing system.
    \item Testing the algorithms to verify their effectiveness in real-world scenarios.
\end{itemize}
Developing these algorithms enhanced problem-solving abilities and technical expertise.

\subsection{Project management and collaboration}
Finally, the project required effective project management and collaboration skills. This involved:
\begin{itemize}
    \item Planning and organizing tasks to ensure timely completion of milestones.
    \item Collaborating with team members to share knowledge and solve problems collectively.
    \item Documenting progress and results to maintain clear communication and facilitate future work.
\end{itemize}
These skills are vital for the successful execution of any complex project.

In summary, the skills learned during this project encompass a wide range of technical and soft skills, all of which are invaluable for future projects and professional growth.